\documentclass[12pt,conference,onecolumn]{IEEEtran}

\usepackage[hidelinks]{hyperref}

\title{Grapple Gun}
\author{%
\IEEEauthorblockN{Callie Butash}\IEEEauthorblockA{Science \& Engineering\\Manalapan High School\\Englishtown, NJ\\\href{mailto:426cbutash@frhsd.com}{426cbutash@frhsd.com}}\and
\IEEEauthorblockN{Srilekha Dantu}\IEEEauthorblockA{Science \& Engineering\\Manalapan High School\\Englishtown, NJ\\\href{mailto:426sdantu@frhsd.com}{426sdantu@frhsd.com}}\and
\IEEEauthorblockN{Connor Paszkiewiecz}\IEEEauthorblockA{Science \& Engineering\\Manalapan High School\\Englishtown, NJ\\\href{mailto:426cpaszkiewiecz@frhsd.com}{426cpaszkiewiecz@frhsd.com}}}
\date{June 16, 2026}

\newcommand{\keywords}{Spiderman, grapple gun, engineering design, assistive technology, superhero, super-ability}

\usepackage{hyperref}
\makeatletter
\AtBeginDocument{
\hypersetup{%
pdftitle={\@title},
pdfauthor={Callie Butash, Srilekha Dantu, and Connor Paszkiewiecz},
pdfkeywords={\keywords}}}
\makeatother

\begin{document}
\maketitle 

\begin{abstract}
Our project aims to design and build a functional grapple gun inspired by Spider-Man’s ability to retrieve objects from a distance. We are looking to translate this fictional ability by developing an efficient launching and grabbing tool that will be able to launch across a room, latch onto a handheld item, and pull the item back to the user. The mechanism will launch an individual clasping system, inspired by mouse traps and other spring-loaded traps, connected to a rope for retrieval. The base of the machine will be powered by a motor in order to draw the rope and item back to the user. We will explore the kinematics and forces required to launch the claw to a desired item, as well as the processes involved in bringing the item back. A tool like this can be helpful when trying to reach trash and dropped belongings from high places, assisting the physically impaired, and reaching the remote without getting off the couch. 

Part of our design process will consist of looking at what exactly makes for an optimal grapple design, and if that changes depending on the use case. We could consider different mechanisms for the use of a first responder compared to grandparents. We plan to experiment with suction vs. clasping, different strengths and size of rope, and manual vs. automatic launching and retraction. 
\end{abstract}

\begin{IEEEkeywords}
\keywords
\end{IEEEkeywords}

\end{document}
